% ======================================================================
\section{Module Grading Scheme}
\label{s:grading}
% ======================================================================


% ----------------------------------------------------------------------

Each FPix phase 1 upgrade module is given a grade based on various aspects of the testing results.
The current grading scheme is preliminary and expected to evolve through the production process
to account for specific component failure modes seen during production.
\\\\
The current scheme is based on two categories (\iv performance and single pixel defects)
although it can be expanded to include X-ray results and many of the other \fulltest measurements.
\\\\
The \iv performance criteria are two-fold.  
First, the module is graded on the amount of leakage current at the expected operating bias (-150V).
Modules must have $\textrm{I}_{-150\textrm{V}} < 2 \mu \textrm{A}$ to receive an A
or $\textrm{I}_{-150\textrm{V}} < 10 \mu \textrm{A}$ to receive a B.
Modules with $\textrm{I}_{-150\textrm{V}} > 10 \mu \textrm{A}$ receive a C.
Secondly, the breakdown voltage for the module should be higher (more negative) than -150V.
This is determined by looking at the ratio $\textrm{I}_{-150\textrm{V}}/\textrm{I}_{-100\textrm{V}}$.
If the module has not reached the breakdown voltage by -150V, this ratio should be small, 
otherwise it should be large.
Modules with $\textrm{I}_{-150\textrm{V}}/\textrm{I}_{-100\textrm{V}} < 2$ receive an A for this criteria,
all other modules receive a C.
The overall \iv grade for the module is the worse of the two assigned grades (leakage current and breakdown voltage).
\\\\
Single pixel defects are identified using the results of the \alivetest and \bb tests.
A sum per \roc is calculated of all pixels flagged as faulty by either of these tests.
If this sum is less than 1\% of pixels in the \roc, the \roc receives an A grade.
Otherwise, if the sum is less than 4\% of pixels in the \roc, the \roc receives an B grade.
If not, the \roc receives a C grade.
The module grade for single pixel defects is assigned as the grade of the worst \roc.
\\\\
The final module grade is assigned as the worse of the \iv grade and the pixel defect grade.
In this way, each module is given either an A, B, or C grade that is recorded in the documentation server.
