% ======================================================================
\section{Modules Tests}
\label{s:tests}
% ======================================================================

Modules are tested using the pXar software framework.  
More information on pXar can be found at https://twiki.cern.ch/twiki/bin/viewauth/CMS/Pxar.
\\\\
With a few exceptions, plots created by pXar represent data from a single \roc.
Most \roc plots have one entry per pixel, and are seen as 1D distributions
or as 2D distributions ($52\times80$) showing the row and columns of the pixels in the \roc.
For this reason, most plots names contain a ``C'' (short for ``chip'') followed by the  \roc number (0-15).
Since, in principle, tests can be performed multiple times, all plots are appended with a version number.
Together, the template for pXar plot naming is ``PLOT\textunderscore NAME\textunderscore C\#\textunderscore V\#''.
Additionally, pXar often creates 1D distributions from 2D \roc plots.  
These plots have names starting with ``dist\textunderscore'' followed by the name of the original 2D plot.
\\\\
In the sample plots included in this document, \roc 0 is shown as an example.
Analogous plots, produced for each \roc, are included in any pXar output file.

% ----------------------------------------------------------------------

\input{pretest.tex}

\input{aliveTest.tex}

\input{trimTest.tex}

\input{phOptTest.tex}

\input{gainPedTest.tex}

\input{sCurvesTest.tex}

\input{bb3Test.tex}

\input{ivTest.tex}

\input{fulltest.tex}

% ----------------------------------------------------------------------
